### 2018-11-28 chapters/3-results.tex
readability

These results indicate that, when it comes to logistic regression models, L2
regularization with all features may perform better than fewer features
selected by L1, for all of the image types except T₂w. With T₂w,
L1 regularization performed better than L2, suggesting that a subset of
features would perform better than all of them.

>>>>

These results indicate that, when it comes to logistic regression models, all
features weighted by L2 regularization may perform better than fewer features
selected by L1, with the exception of T₂w images. With T₂w, L1 regularization
performed better than L2, suggesting that a subset of features would perform
better than all of them.
